invivoPKfit analysis of CvTdb data

### 2023-01-12 Working Rmds/MainAnalysis.Rmd
Add argument fit_conc_dose to control whether to fit dose-normalized concentrations or non-dose-normalized concentrations.

system.time(
  PK.fit.table.flat <- fit_all(
    data.set = cvt,
    model = "flat",
    modelfun = "analytic",
    preprocess = FALSE,
    optimx_args = list(
      "method" = "bobyqa",
      "itnmax" = 1e6,
      "control" = list("kkt" = FALSE)
    ),
    suppress.messages = TRUE
  )
)

@@

```{r, run_invivoPKfit_1comp}
### do 1-Compartment fit
system.time(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt,
      model = "1compartment",
      modelfun = "analytic",
      preprocess = FALSE,
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
  )
)

@@

```{r, run_invivoPKfit_2comp}
### do 2-Compartment fit
system.time(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt,
      model = "2compartment",
      modelfun = "analytic",
      preprocess = FALSE,
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
    )
)

>>>>

system.time(
  PK.fit.table.flat <- fit_all(
    data.set = cvt,
    model = "flat",
    modelfun = "analytic",
    preprocess = FALSE,
    fit_conc_dose = TRUE,
    rescale_time = TRUE,
    optimx_args = list(
      "method" = "bobyqa",
      "itnmax" = 1e6,
      "control" = list("kkt" = FALSE)
    ),
    suppress.messages = TRUE
  )
)

@@

```{r, run_invivoPKfit_1comp}
### do 1-Compartment fit
system.time(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt,
      model = "1compartment",
      modelfun = "analytic",
      preprocess = FALSE,
         fit_conc_dose = TRUE,
    rescale_time = TRUE,
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
  )
)

@@

```{r, run_invivoPKfit_2comp}
### do 2-Compartment fit
system.time(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt,
      model = "2compartment",
      modelfun = "analytic",
      preprocess = FALSE,
         fit_conc_dose = TRUE,
    rescale_time = TRUE,
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
    )
)
